Symmetric Peer-to-Peer Applications

### 2022-08-20 tpd-22.tex
...

In this work, as indicated in Figure~\ref{fig.table}, our goal is to support
peer-to-peer real-time symmetric execution, while still tolerating offline and
out-of-order event generation.
%
As detailed in Figure~\ref{fig.algos}, peers have independent timelines and
can communicate events directly to each other.
Events are delayed to be able to reach other peers in time.
In the case a deadline is missed, the peer rolls back in time and fast
forwards execution until it reaches real time again.
%
Like Croquet and GALS, peers compute events in sequence using only
deterministic and stateless calls.

TODO
- photon unreal
- time machine
    - paper que eu achei ha um tempo
    - braid

\section{The API \& Middleware}
\label{sec.api}

>>>>

In this work, as indicated in Figure~\ref{fig.table}, our goal is to support
peer-to-peer real-time symmetric execution, while still tolerating offline and
out-of-order event generation.
%
As detailed in Figure~\ref{fig.algos}, peers have independent timelines and
can communicate events directly to each other.
Events are delayed to be able to reach other peers in time.
In the case a deadline is missed, the peer rolls back in time and then fast
forwards execution until it reaches real time again.
%
Like Croquet and GALS, peers compute events in sequence using only
deterministic and stateless calls.

Fusion%
\footnote{Fusion: \url{https://doc.photonengine.com/en-us/fusion}}
is a state synchronization networking library for the Unity game engine.
It provides networked tick-based simulation in two modes: client-server
(\emph{hosted mode}) or peer-to-peer (\emph{shared mode}).
The hosted mode is based on continuous memory snapshots, which allows for
full rollbacks when clients diverge.
However, the shared mode is less powerful and only supports eventual
consistency among clients.
We presume that continuous memory snapshots would be too expensive without a
central server.

Regarding single-user time machines, the video game Braid%
\footnote{\url{Braid: http://braid-game.com/}}
is designed on the assumption that players have unrestricted power to go back
in time.
Like Fusion, it's implementation is based on continuous memory snapshots, and
not deterministic simulation as we propose in this work.

- time machine
    - paper que eu achei ha um tempo
    - braid

\section{The API \& Middleware}
\label{sec.tml}

\section{Application}
\label{sec.app}
